Which of my Transient Type Checks are not (Almost) Free?

### 2019-09-11 paper.tex
Some edits sec. 3.1
Signed-off-by: Stefan Marr <git@stefan-marr.de>

\subsection{The Takikawa Protocol}
The Takikawa evaluation protocol was originally proposed for Typed
Racket, where static vs dynamic typing is set per-module, so $N$ is
the number of modules. The original Takikawa protocol also suggested a sampling strategy, where $10N$ configurations are randomly chosen from the lattice, however the lattice is a binomial distribution, meaning the majority of chosen benchmarks will have around $N/2$ type annotations
Grace, following other languages such as
Reticulated Python \cite{reticPython2014,monotonic2015,Vitousek2017},
allows programmers to choose whether each individual declaration should be type-checked. This means $N$ in Grace is the number of type annotations in the program, and so
checking an entire lattice for even a moderately sized benchmark would be infeasible.  Vitousek et al.\ modified the Takikawa protocol for
these kinds of languages by taking an approach based on sampling
\cite{vitousek-transient-arXive-2019}.  The Takikawa-Vitousek protocol
divides the number of type annotations in a fully-typed program into
a maximum of 100 intervals, and then randomly generates ten programs within
each interval by erasing type annotations.
However, this approach was designed for benchmarks with large numbers of type annotations, as well as for a larger sample size than our work.

@@

Unlike such prior work, we wish to identify which type annotations cause anomalies,
% To investigate Moth's support for transient type checks further, 
thus we adapted the Takikawa protocol
and took inspiration from the Takikawa-Vitousek variant.
For each benchmark, we generated 100 partially typed versions,
or fewer if the benchmark has less than 11 types.
We did an even split so that for each $i \ge 1$ and $i$ < $N$, we generated roughly the same number of configurations with $i$ type annotations. We used Robert Floyd's sampling algorithm \cite{Bentley:1987:PPS:30401.315746} to randomly choose the type annotations each configuration contained, and we ensured that no duplicate configurations were generated. In addition to these, we tested fully untyped and typed versions, for a total of 102 configurations per benchmark (or 97 in the case of our Storage benchmark, since it only has 10 type annotations).

>>>>

\subsection{The Takikawa Protocol}
The Takikawa evaluation protocol was originally proposed for Typed
Racket, where static vs dynamic typing is set per-module, so $N$ is
the number of modules. The original Takikawa protocol also suggested a sampling strategy, where $10N$ configurations are randomly chosen from the lattice, however the lattice is a binomial distribution, meaning the majority of chosen benchmarks will have around $N/2$ type annotations.

Grace allows programmers to choose for each individual declaration whether it should be type-checked, and thus follows languages such as
Reticulated Python \cite{reticPython2014,monotonic2015,Vitousek2017}.
This means in Grace $N$ is the number of type annotations in the program.
This makes it infeasible to checking an entire lattice, even for a moderately sized benchmark.
Vitousek et al.\ therefore modified the Takikawa protocol for
these kinds of languages by taking an approach based on sampling
\cite{vitousek-transient-arXive-2019}.  The Takikawa-Vitousek protocol
divides the number of type annotations in a fully-typed program into
a maximum of 100 intervals, and then randomly generates ten programs within
each interval by erasing type annotations.
However, this approach was designed for benchmarks with large numbers of type annotations, as well as for a larger sample size than our work.

@@

Unlike prior work, we wish to identify which type annotations cause anomalies,
% To investigate Moth's support for transient type checks further, 
and thus we adapted the Takikawa protocol
and took inspiration from the Takikawa-Vitousek variant.
For each benchmark, we generated 100 partially typed versions,
or fewer if the benchmark has less than 11 types.
We did an even split so that for each $i \ge 1$ and $i$ < $N$, we generated roughly the same number of configurations with $i$ type annotations. We used Robert Floyd's sampling algorithm \cite{Bentley:1987:PPS:30401.315746} to randomly choose the type annotations each configuration contained, and we ensured that no duplicate configurations were generated. In addition to these, we tested fully untyped and typed versions, for a total of 102 configurations per benchmark (or 97 in the case of our Storage benchmark, since it only has 10 type annotations).
